Size-differentiated Export \add{Flux} in Different Dynamical Regimes in the Ocean

### 2020-06-26 Submission_and_reviews/response_to_reviewers.tex

	\item Explain why you examine the dependence between these different metrics, e.g. something like "we explore the sensitivity of X and Y to the particle size spectrum ..... We consider three distributions with slopes of Z, ZZ.." etc.
		{\color{blue} An introductory sentence was added in ection 2.2.3 to clarify the link between the method and the study's objective.\\}
\end{itemize}

\section*{Minor comments:}
\begin{itemize}
	\item Can you specify if and how equation 9 differs from the traditional Martin curve?
	{\color{blue} A good reference for this would be Cael and Bisson (2018) in \textit{frontiers in Marine Science}. The model used here is an exponential model, as opposed to the "Martin Curve" that relies on a power-law model. The Martin curve implicitely includes a decrease of the remineralization rate with time that is not considered in the exponential model.\\}

	\item L40: the last sentence of the first paragraph is vague and unnecessary. I would delete it.
	{\color{blue} text was modified\\}
	\item L 162: Problem with reference Laboratory, 2018?
	{\color{blue} Reference was fixed\\}
	\item Figures 7 and 8. Please label the size classes on the insert or at least mention the colors-size relationship in the caption.
	{\color{blue} To avoid overcrowing the figures, the color coding is included in the caption for figures 6-8.\\}

	\item The model data used in this study should be made available as requested by AGU standards.
	{\color{blue} The size of the data files exceed a few Terabytes due to the high-resolution simulation,  the very large number of particles tracked, and the number of experiments conducted. We were not able to identify a platform that would host such a large volume of data in a sustained way, and guaranteeing public access, and not for a lack of trying. We would happily consider any suggestions on that issue, as this is a re-occuring challenge in high-resolution modelling.\\}
\end{itemize}
